Welfare Expectations Across U.S. Economic Cycles

### 2024-04-24 paper/paper.qmd
Update structure in introduction

Public attitudes towards government welfare programs fluctuate with economic conditions, swinging from calls for austerity during prosperous times to demands for increased support in downturns. This study investigates whether there is a consistent trend of advocating for reduced welfare spending in periods of economic prosperity and whether there's a noticeable shift towards supporting more government welfare provisions during downturns, as seen during the 1982 recession and the 2020 COVID-19 pandemic. Importantly, we explore whether this trend is consistent across all public segments or if attitudes vary among different demographic groups through various journal research.

@@

The structure of this paper starts with the current [Introduction] to explain the overall logic and content. The subsequent [Data] section outlines our methods and data-cleaning efforts. In the [Model] section, we use a linear regression model to further analyze the number of public responses to "too little" of welfare since 1972. The [Results] section presents findings on public welfare perceptions under different economic conditions. In [Discussion], we interpreted within the larger context of welfare policy and public expectations and are expected to trigger reflections on the study's limitations and potential directions for future research. Finally, we synthesize our main insights in [Conclusion] to highlight the urgent need for nuanced and adaptable welfare policies. [Appendix] provides further model details supporting our analysis.

@@

This paper analyzes data from the NORC General Social Survey (GSS) at the University of Chicago, specifically selecting the “welfare” dataset from 1972 to 2022. Our study mainly enable a comparison of public perceptions of welfare adequacy in the United States. We will also give examples of some specific years for analysis, including 1980, 2018, the normal economic years, and 1982, 2021, the years when recession occurred.
\break

>>>>

Public attitudes towards government welfare programs fluctuate with economic conditions, swinging from calls for austerity during prosperous times to demands for increased support in downturns. This study investigates whether there is a consistent trend of advocating for reduced welfare spending in periods of economic prosperity and whether there is a noticeable shift towards supporting more government welfare provisions during downturns, as seen during the 1982 recession and the 2020 COVID-19 pandemic. Importantly, we explore whether this trend is consistent across all public segments or if attitudes vary among different demographic groups through various journal research.

@@

The structure of this paper starts with the current [Introduction] to explain the overall logic and content. The subsequent [Data] section outlines our methods and data-cleaning efforts. In the [Model] section, we use a linear regression model to further analyze the number of public responses to "too little" welfare since 1972. The [Results] section presents findings on public welfare perceptions under different economic conditions. In [Data and Model Limitations] we mainly explain the immature aspects of data and models for analysis results. In [Discussion], we interpreted within the larger context of welfare policy and public expectations to reflect on the study's limitations and potential directions for future research. Finally, we synthesize our main insights in [Conclusion] to highlight the urgent need for nuanced and adaptable welfare policies. [Appendix] provides further model details supporting our analysis.

@@

This paper analyzes data from the NORC General Social Survey (GSS) at the University of Chicago, specifically selecting the “welfare” dataset from 1972 to 2022. Our study mainly enable a comparison of public perceptions of welfare adequacy in the United States. We will also give examples of some specific years for analysis, including 1980, 2018, the normal economic years, and 1982, 2021, the years when recession occurred.
